---
title: "testing-functions"
format: html
editor: visual
execute: 
  warning: false
---

```{r}
library(testthat)
library(tidyverse)
```

## Function Testing

install.packages(c("testthat", "devtools", "remotes"))

```{r}
#making a function when you plug in a dataframe 
mean_range <- function(df) {
  
  # calculating the mean of each column in our data frame, then find min and max of that
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE)
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  # I want a vector returned 
  return(c(col_mean_min, col_mean_max))
}
```

```{r}
#let's try this out
mean_range(mtcars)

mean_range(faithful)
```

-   errors we could look for

    -   should always be numeric

    -   should always be a vector

## Write some unit tests for previous example

```{r}
# if i apply function mean_range on mtcars the vector length should always be 2, will return nothing if correct, if you test with 3 you get error
expect_length(mean_range(mtcars), 2)

# expect_length(mean_range(mtcars), 3), will not render if there is a break
```

```{r}
# if i apply function mean_range on mtcars the vector length should always be double (since it is numerics in vector), will return nothing if correct, if you test with "character" you get error
expect_type(mean_range(mtcars), "double")
```

```{r}
# the first number in vector should always be less than the second number in the vector, is this true for the data frame
expect_true(mean_range(mtcars)[1] < mean_range(mtcars)[2] )
```

## Afternoon Interactive

```{r}
# want to use function made in other folder so need to indicate where to look being from the beginning of the working directory

source(here::here("src", "name_cart.R"))

name_cart("enchilada", "hawk")
```

```{r}
source(here::here("src", "cork_oak_growth.R"))

height_t2(height_t1 = 20, t1 = 4, t2 = 19)
```

## Making packages

when making packings click in middle of function in document and go to code and choose insert roxygenskeleton to make formatting for documentation for functions in packages
